Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/state01.tex

\ac{WebRTC} aims to provide a standard platform for real-time audio and video on the Web. It arrives at a time when several proprietary products are well established.
\emph{Skype}\footnote{\url{http://www.skype.com/}} is an application that allows video, voice and instant messaging communication over proprietary protocols, its main strength are the amount of users that are using it nowadays and the ability to perform voice calls to the \ac{PSTN}. But compared to \emph{Skype}, \ac{WebRTC} applications don't need to be pre-installed.

\emph{Google Hangouts}\footnote{\url{http://plus.google.com/hangouts}} is another popular video conference web application. 
In the past, in order to use \emph{hangouts} on a web browser a plug-in had to be installed, nowadays hangouts is using \ac{WebRTC}. \emph{Google Hangouts} supports viewing videos on \emph{youtube} synchronously, drawing collaboratively, creating music and playing multi-player games. These applications are implemented with \emph{Adobe Flash}.

>>>>

\ac{WebRTC} aims to provide a standard platform for real-time audio and video on the Web. It arrives at a time when several proprietary products are well established.
\emph{Skype}\footnote{\url{http://www.skype.com/}} is an application that allows video, voice, instant messaging and multi-party communication over proprietary protocols, its main strength are the amount of users that are using it nowadays and the ability to perform voice calls to the \ac{PSTN}. But compared to \emph{Skype}, \ac{WebRTC} applications don't need to be pre-installed.

\emph{Google Hangouts}\footnote{\url{http://plus.google.com/hangouts}} is another popular video multi-party conference web application. 
In the past, in order to use \emph{hangouts} on a web browser a plug-in had to be installed, nowadays hangouts is using \ac{WebRTC}. \emph{Google Hangouts} supports viewing videos on \emph{youtube} synchronously, drawing collaboratively, creating music and playing multi-player games. These applications are implemented with \emph{Adobe Flash}.
